Individual ABC Fits

### 2024-01-23 Model/abc_hier.qmd
script tweaks for alt fits

ind_fits <- readRDS(here::here("data/indv_sim/ind_abc_ss_1000_ng100_bufp55.rds"))

@@

post_tabs$et_sum |> select(condit,Fit_Method,Avg_ALM_error, Avg_EXAM_error) |> filter(Fit_Method=="Test")

@@

>>>>

#ind_fits <- readRDS(here::here("data/indv_sim/ind_abc_ss_1000_ng100_bufp55.rds"))

ind_fits <- readRDS(here::here("data/indv_sim/ind_abc_2000_ng100_buf5.rds"))

@@

post_tabs$et_sum |> select(condit,Fit_Method,Avg_ALM_error, Avg_EXAM_error) |> filter(Fit_Method=="Test Only")

@@

## Distributions: 
```{r, fig.width=12, fig.height=17}
#| eval: true
plot_sampled_posterior(ind_fits)
plot_indv_posterior(ind_fits_df)

ind_fits_df |> filter(id %in% ids2, Fit_Method=="Test & Train") |> 
  ggplot(aes(x=c)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(id~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of c")

ind_fits_df |> filter(id %in% ids2, Fit_Method=="Test & Train") |> 
  ggplot(aes(x=lr)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(id~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of c")

ind_fits_df |> filter(id %in% idsBad, Fit_Method=="Test & Train") |> 
  ggplot(aes(x=c)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(id~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of c")

ind_fits_df |> filter(id %in% idsBad, Fit_Method=="Test & Train") |> 
  ggplot(aes(x=lr)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(id~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of c")
